% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Experience}{\faLaptop}
\begin{projects}
    \project
    {Ooma}{Vancouver, British Columbia, Canada - (Hybrid)}{2022 - Current}
    {\website{https://www.ooma.ca/}{ooma.ca}}
    {Ooma, Inc. is a publicly traded telecommunications company based in Silicon Valley, California, offering communication services including Voice.
    \begin{itemize}
        \item Improved the page load by ~70\% performance of the Call Center screen by optimizing the react component by using debugging tools like React Profiler and Chrome Devtools.
        \item Merged the Admin Portal application to host app, Commland using the front-end microservices library Single-spa resulting in the reduction of duplicate code base by ~7\%.
        \item Developing reusable React Functional components saving significant development time by almost 50\% across 4 projects.
        \item Collaborated with automation engineers to optimize testing processes, reducing regression issues by 40\% and improving release efficiency.
        \item Developed a reusable autocomplete input component which auto-fills the address parts in different fields that fetches the real addresses using Google Maps API which helped in improving the user experience.
        \item Planning and building applications' data layer, caching, routing strategies and building shared component library using React and Next.js.
        \item Documenting code, contributing to style guides, and working in close coordination with various team associates.
        \item Creating and maintaining efficient API queries using GraphQL and Redux Tooltip. 
        \item Led the migration of a complex phone system admin portal and unified telecom application from JQuery and Javascript to React.js SPA.
        \item Redesigning and implementing modern UI/UX principles, improving application responsiveness, and enhancing maintainability.
        \item Worked closely with QA in adapting components in support of the automated testing suite.
        \item Collaborated with design and business teams to align requirements with the broader design system across multiple applications.
        \item Providing technical feedback and estimates, allowing for streamlined development processes and on-time project delivery.
        \item Optimized Cypress.js test suite to improve test execution times, leading to a more efficient and effective testing process
    \end{itemize}}
    {ReactJS, NextJS, Typescript, GraphQL, Redux Toolkit (RTK Query), Jest, React testing Library, NodeJS, MUI, Styled Components}

    \project
    {Simpplr}{Toronto, Ontario, Canada - (Remote)}{2019 - 2022}
    {\website{https://youtu.be/JWazalheGhA?si=52ERWiE8SqbFnIvp&t=37}{Video}}
    % {\website{https://youtu.be/JWazalheGhA}{Youtube Demo Link}}
    {Simpplr is a purpose-built SAAS platform to help your employees collaborate across departments and stay connected to the broader organization.
    \begin{itemize}
        \item I led and developed the native WYSIWYG editor on the micro-frontend architecture (MFE) to replace the existing library. This benefited from avoiding the yearly cost of using the third-party library by a couple of hundred dollars and reduced the host app's code base by 5\% by converting the code base in MFE, also providing a better feature-packed UI for the end users.
        \item Developed the "Native Video" feature that enabled the users to upload and play videos into the different parts of the application, e.g. while composing new posts. This benefited in reducing the dependency on third-party video service providers like YouTube, Vimeo, etc, instead them serving them from the private cloud platform.
        \item Developing new features using React and dependable UI libraries Build reusable components.
        \item Translating designs and wireframes into high-quality code, optimizing components for maximum performance across.
        \item Creating and updating unit test cases for each delivered module with maximum coverage using tools like Jest, and React Testing Library.
        \item Documenting and maintaining the technical workflows and specifications during the feature development on the Confluence platform.
        \item Gathering requirements for product owners, collaborating and having discussions for grooming requirements, followed by work estimations.
        % \item Reviewing on Pull Requests raised by peers to improve the code quality, discussing them for learning.
        \item Mentoring team members and peers for any clarity on processes and projects.
    \end{itemize}}
    {ReactJS, NextJS, Typescript, Redux, React Query, Webpack, Jest, React testing Library, Cypress, Javascript, NodeJS}

    \newpage
    \project
    {RSG Media}{New Delhi, India - (Onsite)}{2016 - 2019}
    {\website{https://promo.rsgmedia.com}{Prophet 2.0}}
    {Analytics product used by Viacom Media Networks and others to keep track of ROI, reach, etc. of promo aired on the different media platforms.
    \begin{itemize}
        \item Used promo data to render them in different charts like Bar charts, and pie charts to better visualization for users.
        \item Used ParamQuery grid library to show and edit complex promo data in table format.
        \item Built and maintained GUIs using Handlebars/ ReactJS to provide usability to business data.
        \item Created RESTful API endpoints using NodeJS, and ExpressJS.
        \item Managing the versions and branches to staging and production servers using tools like GIT, sourcetree.
        \item Discussed, analyzed and strategized product design with Product Managers, the UX team and Business Managers.
        \item Tracking and resolving tickets for issues raised on the bug reporting tool (Bitbucket).
        % \item Mentored junior developers on JavaScript, and Web Application Development.
    \end{itemize}}
    {jQuery, Javascript, NodeJS, ReactJS, MySQL, DashDB, ParamQuery Grid}

    \project
    {9.9 Media}{Noida, India - (Onsite)} {2014 - 2016}
    {\website{https://www.digit.in}{digit.in}}
    {\begin{itemize}
        \item Implementing trending UI technologies like Lazyloading, InfineScroll, etc.
        \item Deploying and rendering Ads dynamically using Google API, etc.
        \item Implemented and Launched Accelerated Mobile Pages (AMP) version of news, stories to instantly render on google.com
        \item Created the Product Guru page for searching the products based on preference weight-age and showing the result on the fly.
    \end{itemize}}
    {JavaScript, jQuery, AngularJS, HTML, CSS}
    
    % \project
    % {DigitFix Partners Mobile App} {2016}
    % {\website{https://play.google.com/store/apps/details?id=com.ionicframework.myapp259956}{Google Play Link}}
    % {\begin{itemize}
    %     \item HTML prototyping for new components in the application and integrating the prototypes with AngularJS code.
    %     \item Customizing mobile application using Cordova APIs.
    %     \item Using and Deploying AngularJS Cross domain server calls.
    %     \item Worked on several UI enhancements and fixes of the current screens.
    %     \item Versioning the application and pushing it to Google Play Store followed by generating APKs.
    % \end{itemize}}
    % {JavaScript, AngularJS, Ionic Framework}
    
    % \emptySeparator
    % \project
    % {DigitFix Web Application} {2016}
    % {\website{https://www.digitfix.com}{digitfix.com}}
    % {\begin{itemize}
    %     \item Implementing UI design to AngularJS components.
    %     \item Routing and linking application using AngularJS StateProvider module.
    %     \item Reading and implementing Google Maps API for pinning and searching mobile service centers.
    %     \item Making optimized server calls using AngularJS services.
    % \end{itemize}}
    % {JavaScript, AngularJS}

    \project
    {Nineteen Apparels} {New Delhi, India - (Onsite)} {2013 - 2014}
    {\website{https://www.shopnineteen.com}{shopnineteen.com}}
    {\begin{itemize}
        \item Designed and developed custom Magento themes to enhance UI/UX, ensuring responsiveness and accessibility. Also, Custom Designed and developed custom Magento themes to enhance UI/UX, ensuring responsiveness and accessibility.
        \item Improvising page load time and persistent load time by optimizing, and minifying js, CSS and other assets.
        \item Optimized Magento themes for faster page load times by minifying CSS/JS, implementing lazy loading, and improving asset management.
        % \item Custom Designed and developed custom Magento themes to enhance UI/UX, ensuring responsiveness and accessibility.
        \item Ensured that Magento themes adhered to SEO best practices and accessibility guidelines for better search ranking and user experience.
        % \item Integrating responsive theme using tools like Bootstrap etc.
        % \item Making the UI responsive using CSS media queries.
        % \item Integrated elements like carousal to make the website appealing.
    \end{itemize}}
    {PHP, Magento, JQuery, Javascript, MySQL, HTML, CSS}

    \project
    {Diametric Solutions and others} {New Delhi, India - (Onsite)} {2012 - 2013}
    {}
    % {\begin{itemize}
    %     \item iamnineteen.com
    %     \item kippandludwig.com 
    %     \item theartjewellery.com
    %     \item pennywisefilms.com
    %     \item shuttlecockboys.com
    %     \item diametricsolutions.com
    %     \item abptechinc.com
    %     \item babajiayurveda.in
    %     \item indianbizmart.com
    % \end{itemize}}
    {iamnineteen.com, kippandludwig.com , theartjewellery.com, pennywisefilms.com, shuttlecockboys.com, diametricsolutions.com, abptechinc.com, babajiayurveda.in, indianbizmart.com
    {\begin{itemize}
        \item Developing web pages quickly and effectively using HTML 5, CSS 3 and JS.
        \item Making the responsive layout using Flexbox, CSS Media Queries, CSS Grigs, frameworks like Bootstrap, MUI, etc.
        \item Good understanding of layout design, colours and typographical fundamentals.
        \item Checking and debugging cross-browser compatibility issues.
        \item Making the web application robust using an object-oriented design approach.
        % \item Validating and fixing accessibility issues.
        \item Participate in requirements analysis, code reviews and project releases.
        \item Following the agile process which encourages new changes effectively using Jira.
        \item Experience in Internationalization and localization libraries like i18next.
        \item Full stack web development covering all dimensions using NodeJs, React, API interactions and API
    \end{itemize}} }
    {}
\end{projects}
